Dynamic Topic Modeling for Voice Dialogues

### 2024-05-24 paper/main.tex
paper fin

The main objectives of the research work is to create and apply Dynamic Topic Modeling pipeline based on LLM for topic extraction for audio and text dialogues. 
To solve this problem, you will need to complete the following tasks 
\begin{enumerate}
    \item The identification of suitable datasets for experiments;
    \item The investigation of the best suitable open-source solutions for speaker diarisation, dialogue clustering, topic extraction and topic evolution;
    \item The exploration of the possibilities of using Large Language Models for some stages and the selection of models suitable for training in limited resources;
    \item The selection of appropriate metrics and measurement of the quality of the approaches used at each stage;
\end{enumerate}

@@

Speaker diarisation is the process of automatically segmenting and identifying different speakers in an audio recording. 
The goal of speaker diarisation is to divide the audio stream into non-homogeneous segments, each segment corresponding to a specific speaker or speaker turn.

@@

The pipeline of dynamic topic modelling of audio dialogues, which will be considered in this paper, is divided into several main stages. 
These include ASR, dialogue segmentation, topic extraction and topic evolution.

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns & Avg tokens \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13 & 239 \\ 
            Tiage &  7939/-/1000 & 14.7  & - \\ 
            \hline
            Product Meetings (AMI) & 137 & 535.6 & - \\ 
            Academic Meetings (ICSI) & 59 & 819.0 & - \\ 
            \hline
        \end{tabular}
    \end{center}
    \captionof{table}{Datasets}
\end{table}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \cline{2-7}
         & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & \cellcolor{green!20} 0.446 & \cellcolor{green!20} 0.458 & \cellcolor{green!20} 0.378 \\
        TeT + BERT & \cellcolor{green!20} 0.425 & \cellcolor{green!20} 0.439 & \cellcolor{green!20} 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        Our method & 0.4465 & 0.4575 & 0.367 & 0.5071 & 0.5219 & 0.430 \\ 
        Our method + fine-tune & \cellcolor{green!40} 0.4094 & \cellcolor{green!40} 0.4048 & \cellcolor{green!40} 0.7374 & \cellcolor{green!40} 0.4361 & \cellcolor{green!40} 0.44510 & \cellcolor{green!40} 0.7421 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{AMI} & \multicolumn{3}{| c |}{ICSI} \\
        \cline{2-7}
        & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.3641 & 0.762 & 0.730 & 0.309 \\
        GraphSeg & 0.875 & 0.750 & 0.422 & 0.810 & 0.756 & 0.275 \\
        TextTilling & Pk & wd & f1 & Pk & wd & f1 \\
        TeT + BERT & Pk & wd & 0.443 & Pk & wd & 0.158 \\ 
        \hline
        Our method & \cellcolor{green!20} 0.6447 & \cellcolor{green!20} 0.7394 & \cellcolor{green!20} 0.551 & \cellcolor{green!20} 0.6148 & \cellcolor{green!20} 0.6731 & \cellcolor{green!20} 0.779 \\ 
        Our method + fine-tune & \cellcolor{green!40} 0.5279 & \cellcolor{green!40} 0.6932 & \cellcolor{green!40} 0.610 & \cellcolor{green!40} 0.5842 & \cellcolor{green!40} 0.5932 & \cellcolor{green!40} 0.815 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Dialogue segmentation experiments}
\end{center}

@@

Summarizing all the results of the article:
\begin{itemize}
    \item Suitable datasets were selected, experiments were carried out on them at all stages and quality metrics of the selected algorithms were obtained;
    \item Among the available solutions, the best available metrics were selected. Experiments were carried out with each of the algorithms at each stage on ready-made models, pre-trained and trained from scratch. The best models were added to the final pipeline;
    \item At the topic extraction stage, a study was conducted on the use of LLM. The best open-source LLMs were selected for experiments with zero-shot, feat-shot and fine-tuning. Using LLM at this stage, it was possible to increase the metrics for audio dialogues. \\
     - Topic Diversity was increased around 10 times, and Topic Coherence is about the same value compared to BertTopic and LSA as shown in \ref{table:topicextr}; \\
     - As for the textual dialogues worth noting that the increase ща Topic Deversity is less and on Topic Coherence BertTopic sometimes shown higher results.
\end{itemize}

>>>>

The main objectives of the research work is to create and apply Dynamic Topic Modeling pipeline based on LLM for topic extraction for audio and text dialogues. 
To solve this problem, you will need to complete the following tasks 
\begin{enumerate}
    \item The identification of suitable datasets for experiments;
    \item The investigation of the best suitable open-source solutions for speaker diarization, dialogue clustering, topic extraction and topic evolution;
    \item The exploration of the possibilities of using Large Language Models for some stages and the selection of models suitable for training in limited resources;
    \item The selection of appropriate metrics and measurement of the quality of the approaches used at each stage;
\end{enumerate}

@@

Speaker diarization is the process of automatically segmenting and identifying different speakers in an audio recording. 
The goal of speaker diarization is to divide the audio stream into non-homogeneous segments, each segment corresponding to a specific speaker or speaker turn.

@@

The pipeline of dynamic topic modelling of audio dialogues, which will be considered in this paper, is divided into several main stages. 
These include speaker diarization, dialogue segmentation, topic extraction and topic evolution.

@@

\begin{table}[htb]
    \begin{center}
        \begin{tabular}{ | c | c | c | c |} 
            \hline
            dataset & train/val/test & Avg Turns \\ 
            \hline
            SuperDialseg & 6984/1322/1322 & 13  \\ 
            Tiage &  7939/-/1000 & 14.7 \\ 
            \hline
            Product Meetings (AMI) & 137 & 535.6 \\ 
            Academic Meetings (ICSI) & 59 & 819.0 \\
            \hline
        \end{tabular}
    \end{center}
    \captionof{table}{Datasets}
\end{table}

@@

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \cline{2-7}
         & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & \cellcolor{green!20} 0.446 & \cellcolor{green!20} 0.458 & \cellcolor{green!20} 0.378 \\
        TeT + BERT & \cellcolor{green!20} 0.425 & \cellcolor{green!20} 0.439 & \cellcolor{green!20} 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        Our method & 0.447 & 0.457 & 0.367 & 0.507 & 0.522 & 0.430 \\ 
        Our method + fine-tune & \cellcolor{green!40} 0.409 & \cellcolor{green!40} 0.405 & \cellcolor{green!40} 0.737 & \cellcolor{green!40} 0.436 & \cellcolor{green!40} 0.445 & \cellcolor{green!40} 0.742 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{AMI} & \multicolumn{3}{| c |}{ICSI} \\
        \cline{2-7}
        & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.364 & 0.762 & 0.730 & 0.309 \\
        GraphSeg & 0.875 & 0.750 & 0.422 & 0.810 & 0.756 & 0.275 \\
        TextTilling & 0.867 & 0.730 & 0.429 & 0.805 & 0.753 & 0.295 \\
        TeT + BERT & 0.794 & 0.705 & 0.510 & 0.798 & 0.720 & 0.158 \\ 
        \hline
        Our method & \cellcolor{green!20} 0.645 & \cellcolor{green!20} 0.739 & \cellcolor{green!20} 0.551 & \cellcolor{green!20} 0.615 & \cellcolor{green!20} 0.673 & \cellcolor{green!20} 0.779 \\ 
        Our method + fine-tune & \cellcolor{green!40} 0.528 & \cellcolor{green!40} 0.693 & \cellcolor{green!40} 0.610 & \cellcolor{green!40} 0.584 & \cellcolor{green!40} 0.593 & \cellcolor{green!40} 0.815 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Dialogue segmentation experiments}
\end{center}

@@

Summarizing all the results of the article:
\begin{itemize}
    \item Suitable datasets were selected, experiments were carried out on them at all stages and quality metrics of the selected algorithms were obtained;
    \item Among the available solutions, the best available metrics were selected. Experiments were carried out with each of the algorithms at each stage on ready-made models, pre-trained and trained from scratch. The best models were added to the final pipeline;
    \item In terms of dialogues segmentation, BERT was trained specifically for audio dataset to calculate depth scores and gave better results than TextTililng by 0.1 for f1 metrics and 0.15 less for pk and windiff.
    \item At the topic extraction stage, a study was conducted on the use of LLM. The best open-source LLMs were selected for experiments with zero-shot, feat-shot and fine-tuning. Using LLM at this stage, it was possible to increase the metrics for audio dialogues. \\
     - Topic Diversity was increased around 10 times, and Topic Coherence is about the same value compared to BertTopic and LSA as shown in \ref{table:topicextr}; \\
     - As for the textual dialogues worth noting that the increase of Topic Deversity is less and on Topic Coherence BertTopic sometimes shown higher results.
\end{itemize}
